---
fig-height: 7
fig-width: 6
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
source("global.R")
library(patchwork)
```

# Exploratory and diagnostic displays

Displays of exploratory or diagnostic plots have several figures
sharing a common theme arranged on a single page. Displays can
include ETA, NPDE or CWRES based plots. 


## NPDE-based diagnositcs

Use `npde_panel()` to create a standardized panel of common
NPDE-based diagnostics

```{r}
#| fig-height: 7
#| fig-width: 5 
data <- pmplots_data_obs()

npde_panel(data)
```

### Tag levels 

You can label the panels with the `plot_annotation()` 
function from the patchwork package

```{r}
npde_panel(data) + 
  plot_annotation(tag_levels = "A")
```

### NPDE scatter

This display includes just a subset of the diagnostics which are scatter plots

```{r}
npde_scatter(data)
```

### NPDE histogram and qq plot

This display is the complement of the scatter plots

```{r}
#| fig-width: 5
npde_hist_q(data)
```

## NPDE versus covariate

You can enter a mix of categorical and continuous covariates: here, 
`WT` and `SCR` are continuous covariates and `RF` and `CPc` are 
categorical

```{r}
covs <- c(
  "WT  // Weight (kg)", 
  "SCR // Serum creatinine (mg/dL)", 
  "RF  // Renal group", 
  "CPc // Child-Pugh"
)
npde_covariate(data, covs)
```


## CWRES-based diagnostics

There are a equivalent set of displays which show `CWRES` rather than 
`NPDE`

```{r}
cwres_panel(data) 
```

### CWRES scatter

```{r}
cwres_scatter(data)
```

### CWRES histogram and qq plot

```{r}
#| fig-width: 5
cwres_hist_q(data)
```

## CWRES versus covariate

```{r}
covs <- c(
  "WT  // Weight (kg)", 
  "SCR // Serum creatinine (mg/dL)", 
  "RF  // Renal group", 
  "CPc // Child-Pugh"
)
cwres_covariate(data, covs)
```


## ETA versus covariate

These displays are created with `eta_covariate()`. Since there are typically several ETAs to look at, this function returns a list of 
arranged plots

```{r}
id <- pmplots_data_id()
```

```{r}
etas <- eta_col_labs(CL, V2, KA)
etas
```

For ETA diagnostics, we can plot versus a mix of categorical and 
continuous covariates

```{r}
covs <- c(
  "WT // Weight (kg)", 
  "AAG // AAG (mg/dL)", 
  "AGE // Age (years)", 
  "STUDYc // Study", 
  "RF // Renal function", 
  "CPc // Child-Pugh"
)

cov <- eta_covariate(id, x = covs , y = etas, byrow = FALSE) 
```

By default, the plots are collected by the `ETA`

```{r}
names(cov)

cov$ETA1
```

Use the `transpose` argument to collect by the covariate

```{r}
cov <- eta_covariate(id, covs, etas, transpose = TRUE, ncol = 1)

names(cov)
```

```{r}
cov$WT
```





