---
fig-height: 7
fig-width: 6
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
source("global.R")
library(patchwork)
```

# Exploratory and diagnostic displays

Displays of exploratory or diagnostic plots have several figures
sharing a common theme arranged on a single page. These displays tend to 
have fixed composition and arrangement, with some customization allowed. If 
you want a totally custom display, it is best to create your own from base
pmplots functions, arranging as you like with the patchwork package. 

Displays can include ETA, NPDE or CWRES based plots. 


## NPDE-based diagnositcs

Use `npde_panel()` to create a standardized panel of common
NPDE-based diagnostics

```{r}
#| fig-height: 7
#| fig-width: 5 
data <- pmplots_data_obs()

npde_panel(data)
```

### Tag levels 

You can label the panels with the `plot_annotation()` 
function from the patchwork package

```{r}
npde_panel(data) + 
  plot_annotation(tag_levels = "A")
```

### NPDE scatter

This display includes just a subset of the diagnostics which are scatter plots

```{r}
npde_scatter(data)
```

### NPDE histogram and qq plot

This display is the complement of the scatter plots

```{r}
#| fig-width: 5
npde_hist_q(data)
```

## NPDE versus covariate

You can enter a mix of categorical and continuous covariates: here, 
`WT` and `SCR` are continuous covariates and `RF` and `CPc` are 
categorical

```{r}
covs <- c(
  "WT  // Weight (kg)", 
  "SCR // Serum creatinine (mg/dL)", 
  "RF  // Renal group", 
  "CPc // Child-Pugh"
)
npde_covariate(data, covs)
```


## CWRES-based diagnostics

There are a equivalent set of displays which show `CWRES` rather than 
`NPDE`

```{r}
cwres_panel(data) 
```

### CWRES scatter

```{r}
cwres_scatter(data)
```

### CWRES histogram and qq plot

```{r}
#| fig-width: 5
cwres_hist_q(data)
```

## CWRES versus covariate

```{r}
covs <- c(
  "WT  // Weight (kg)", 
  "SCR // Serum creatinine (mg/dL)", 
  "RF  // Renal group", 
  "CPc // Child-Pugh"
)
cwres_covariate(data, covs)
```


## ETA versus covariate

These displays are created with `eta_covariate()`. Since there are typically several ETAs to look at, this function returns a list of 
arranged plots

```{r}
id <- pmplots_data_id()
```

```{r}
etas <- eta_col_labs(CL, V2)
etas
```

For ETA diagnostics, we can plot versus a mix of categorical and 
continuous covariates

```{r}
covs <- c(
  "WT     // Weight (kg)", 
  "AAG    // AAG (mg/dL)",
  "STUDYc // Study", 
  "RF     // Renal function"
)

cov <- eta_covariate(id, x = covs , y = etas, byrow = FALSE) 
```

By default, the plots are collected by the `ETA`

```{r}
names(cov)

cov$ETA1
```

Use the `transpose` argument to collect by the covariate

```{r}
cov <- eta_covariate(id, covs, etas, transpose = TRUE, ncol = 1)

names(cov)
```

```{r}
cov$WT
```

## Panel as list

You can request one of the panel displays as a list of the 
component plots. In general, you can call the function with 
`_list` suffix. For example, `x` here is a named list of plots

```{r}
#| fig-width: 4
#| fig-height: 4
x <- npde_panel_list(data)
names(x)
x$tad
```

Similar for the covariate plots, but the result will be a 
list of lists

```{r}
#| fig-width: 4
#| fig-height: 4
x <- eta_covariate_list(id, x = covs , y = etas) 
names(x)
names(x$ETA1)
x$ETA1$AAG
```

### Arranging lists of plots

Plots can be arrranged in a grid with `pm_grid()`

```{r}
x <- cwres_panel_list(data)
pm_grid(x, ncol = 2)
```

Or, use `pm_with()` to arrange them using `patchwork` syntax

```{r}
library(patchwork)

names(x)

pm_with(x,  time / (hist+q) / (tad+pred)) 
```

### Rotating axis-tick marks 

Use `rot_xy()` to rotate axis tick marks on a plot. There are
methods for `gg` objects, `patchwork` objects, and lists of 
these objects. 

```{r}
#| fig-height: 6
#| fig-width: 6 
x <- eta_covariate(id, x = covs , y = etas, transpose = TRUE, 
                   ncol = 1) 

x <- rot_xy(x, at = c("STUDYc", "RF"))

pm_with(x, STUDYc | WT)
```

