
```{r setup, include = FALSE}
source("global.R")
```

# dv-pred-ipred


This function will split your dataset up in "chunks" according 
to the columns named in `facets`. Pass the number of `id_per_plot`. 
The return is a list of plots covering all unique values in 
`facets`. 

In this example, we'll just plot 9 subjects in a single plot

```{r}
dd1 <- filter(df, ID <= 9)
```

Please see the `?dv_pred_ipred` help file as there are many arguments
which allow you to customize the output

```{r}
#| fig-height: 6
#| fig-width: 8

dv_pred_ipred(
  dd1, 
  facets = "ID", 
  id_per_plot = 9
)
```

Some arguments to note

- `log_y` - log transformed y-axis
- `angle` - for rotating `x-axis` tick labels
- `xlab` - `x-axis` title
- `ylab` - `y-axis` title
- `nrow` - for arranging facets on a page
- `ncol` - for arranging facets on a page
- `fun` - a function which modifies every plot in the output list

There are also a whole series of arguments for configuring the points 
and lines on the plot for `DV`, `PRED` and `IPRED`.
