
```{r setup, include = FALSE}
source("global.R")
```

# Pairs plots {#sec-pairs}

## General pairs plot

This is a simple wrapper around `GGally::ggpairs` with some customizations that 
have been developed internally at MetrumRG over the years.

```{r}
#| fig-width: 5
#| fig-height: 5
cols <- c("WT//Weight", "ALB//Albumin", "SCR//Serum creat")
pairs_plot(id, cols)
```

One customization we've added is the annotation on the upper triangle, which 
is the `complete.obs` correlation between `x` and `y` along with the number 
of observations. 

## ETA pairs plots

There is also a function called `eta_pairs()` that is identical to the 
`pairs_plot()` function. This might be helpful to remember the function name 
but there is no difference in functionality between `eta_pairs()` and 
`pairs_plot()`. 


## Customized lower triangle

Pass a function that customizes the scatter plots on the lower triangle. This 
function should accept a gg object and add a geom to it

```{r}
my_lower <- function(p) {
  p + geom_point(aes(color = STUDYc)) + 
    geom_smooth(se = FALSE, color = "black")
}
```

```{r}
#| fig-width: 5
#| fig-height: 5
pairs_plot(id, c("WT", "ALB"), lower_plot = my_lower)
```
