---
fig-height: 4.5
fig-width: 4.5
---

```{r setup, include = FALSE}
source("global.R")
```


# Residual plots

## Residuals

### Versus TIME `[res_time]`

```{r}
res_time(df)
```

### Versus TAFD `[res_tafd]`

```{r}
res_tafd(df)
```

### Versus TAD `[res_tad]`

```{r}
res_tad(df)
```

### Versus PRED `[res_pred]`

```{r}
res_pred(df)
```


### Versus continuous `[res_cont]`

```{r}
res_cont(df, x = "WT//Weight (kg)")
```

This function is also vectorized in x.

```{r}
#| fig-height: 6
#| fig-width: 6
res_cont(df, c("WT", "CRCL", "AST")) %>% 
  pm_grid()
```


### By categorical `[res_cat]`

```{r}
dplyr::count(df, STUDYc)

res_cat(df, x = "STUDYc//Study type")
```


### Histogram `[res_hist]`

```{r}
res_hist(df)
```


## WRES

### Versus TIME `[wres_time]`

```{r}
wres_time(df) 
```


### Versus TAFD `[wres_tafd]`
```{r}
wres_tafd(df)
```

### Versus TAD `[wres_tad]`

```{r}
wres_tad(df)
```


### Versus PRED `[wres_pred]`
```{r}
wres_pred(df)
```

### Versus continuous `[wres_cont]`

This function is also vectorized in x.

```{r}
wres_cont(df, x = "WT//Weight (kg)")
```


###  By categorical `[wres_cat]`

```{r}
wres_cat(df, x = "STUDYc//Study type")
```

### Histogram `[wres_hist]`

```{r}
wres_hist(df)
```


### QQ plot `[wres_q]`

```{r}
wres_q(df)
```


## CWRES

### Versus TINE `[cwres_time]`

```{r}
cwres_time(df)
```

### Versus TAFD `[cwres_tafd]`

```{r}
cwres_tafd(df)
```

### Versus TAD `[cwres_tad]`

```{r}
cwres_tad(df)
```

### Versus continuous `[cwres_cont]`

```{r}
cwres_cont(df, x = "WT//Weight (kg)")
```

Vectorized version

```{r}
#| fig-height: 6
#| fig-width: 6
cwres_cont(df, covs) %>% 
  pm_grid(ncol=2)
```


### By categorical `[cwres_cat]`

```{r}
cwres_cat(df, x = "STUDYc//Study type") 
```

```{r}
cwres_cat(
  df, 
  x = "STUDYc//Study type", 
  shown = FALSE
)
```

Vectorized version

```{r}
cwres_cat(
  df, 
  x = c("STUDYc//Study", "RF//Renal Function")
) %>% pm_grid()
```


### Histogram `[cwres_hist]`

```{r}
cwres_hist(df)
```

### Versus PRED `[cwres_pred]`

```{r}
cwres_pred(df)
```

### QQ plot `[cwres_q]`

```{r}
cwres_q(df)
```
