
```{r setup, include = FALSE}
source("global.R")
```

# Wrapped plots

## Setup

Wrapped plots are like the other standardized plots we have 
seen in the gallery so far, but they allow for a simple faceting
using `ggplot2::facet_wrap()`.

:::{.callout-note collapse=true appearance="simple"}

## Preview the data used on this page

The data are identical to the data used for the other series of
plots and do not require any special configuration.


```{r}
head(as.data.frame(df), n=3)
```

:::

## Histogram
```{r}
#| fig-height: 5
#| fig-width: 7
wrap_hist(
  df, 
  x = c("WT", "ALB", "SCR"), 
  scales = "free", 
  bins = 10, 
  ncol = 2
)
```

## ETA versus continuous
```{r}
#| fig-width: 6
#| fig-height: 4
wrap_eta_cont(
  df, 
  y = "ETA1", 
  x = c("WT", "ALB"), 
  scales = "free_x"
)
```

## Continuous on categorical

```{r, fig.height = 5, fig.width = 5}
#| fig-height: 5
#| fig-width: 7
wrap_cont_cat(
  df, 
  y = c("WT", "CRCL", "AAG"), 
  x = "STUDYc", 
  ncol = 2
) 
```

## Continuous on continuous

```{r}
#| fig-height: 5
#| fig-width: 7
wrap_cont_cont(
  df, 
  y = "CWRES" , 
  x = c("WT", "CRCL", "AAG"), 
  ncol = 2, scales = "free_x"
) 
```


## Residuals versus time

```{r}
#| fig-height: 5
#| fig-width: 7
wrap_res_time(
  df, 
  y = c("RES", "WRES", "CWRES"), 
  ncol = 2, scales = "free_y"
) 
```

## DV/PRED and DV/IPRED

```{r}
#| fig-height: 4
#| fig-width: 7
wrap_dv_preds(df, ncol = 2)
```

## Use labels in the strip
```{r}
#| fig-width: 7
#| fig-height: 4
wrap_eta_cont(
  df, 
  y = "ETA1", 
  x = c("WT//Weight (kg)", "ALB//Albumin (g/dL)"),
  scales = "free_x", 
  use_labels = TRUE
)
```

